% LaTeX Resume 

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.4in, top=0.4in, bottom=0.4in]{geometry}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% Uncomment one of the following if you want to change the default font
%
% Sans-serif
% \usepackage[sfdefault]{roboto} % Roboto
% \usepackage[sfdefault]{noto-sans} % Noto Sans
% Serif
% \usepackage{charter} % Charter
% Times New Roman lookalike
\usepackage{newtxtext,newtxmath}

\pagestyle{plain}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Customize link colors
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section Formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting is now consistent with the overall style
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\normalsize
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% This command is now designed to be used within an itemize environment directly
\newcommand{\resumeLink}[2]{\item \href{#1}{#2}}


% Adjust the foot skip to ensure footer content is well-placed
\setlength{\footskip}{20pt} % Increased foot skip for better spacing

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{center}
    \textbf{\Huge \scshape Pratyush Shukla} \\ \vspace{2pt}
    \small 
    \faIcon{github}
    \href{https://github.com/the-praxs}{the-praxs} $|$
    \faIcon{github}
    \href{https://github.com/hawk-praxs}{hawk-praxs} $|$
    \faIcon{linkedin}
    \href{https://linkedin.com/in/praxs}{linkedin.com/in/praxs} $|$
    \faIcon{envelope}
    \href{mailto:pratyush.shukla@outlook.in}{pratyush.shukla@outlook.in} $|$
    \faIcon{phone}
    \href{tel:+918853934890}{+91-8853934890}
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
        \resumeProjectHeading
        {\textbf{New York University} $|$ \footnotesize\emph{M.S. Computer Engineering, GPA - 3.333/4}}{May 2023}

        \resumeProjectHeading
        {\textbf{Lovely Professional University} $|$ \footnotesize\emph{B.Tech (Hons.) Computer Science and Engineering, CGPA - 8.020/10}}{July 2021}

  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++17, SQL, NoSQL, JavaScript, TypeScript, Go, MATLAB, \LaTeX}
     
     \textbf{Tools}{: Git, Docker, PostgreSQL, MongoDB, Node.js, Amazon Web Services (AWS), Microsoft Azure, Isaac Sim, Terraform, Excel}
     
     \textbf{Frameworks}{: Flask, PySpark, FastAPI, PyTorch, LangChain, Autogen, crewAI, Jinja2, STL}
     
     \textbf{Libraries}{: NumPy, SciPy, pandas, sklearn, Beautiful Soup, Pydantic, SQLAlchemy, OpenCV, Transformers, Diffusers, Boost}
     
    }}
 \end{itemize}

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Orangewood Labs} $|$ \footnotesize\emph{AI \& Computer Vision Engineer}}{April 2024 -- Current}
    \resumeItemListStart
      \resumeItem{Leading the \href{https://robogpt.orangewood.co}{RoboGPT} v4 project as an agentic platform for several robot types with real-world and simulation support.}
      \resumeItem{Leading the decentralized AI project on connecting HPC clusters remotely and securely managing them via blockchain technology to provide on-demand, low-cost services to consumers.}
      \resumeItem{Led the migration of the projects from Bitbucket to GitHub as an organization owner by setting up CI/CD pipelines, policies,  and teams, accelerating project management by 2x.}
      \resumeItem{Led R\&D on training a model for the Orangewood 6.5 robotic arm with the HuggingFace LeRobot library on several tasks.}
      \resumeItem{Represented the organization as the lead AI \& Computer Vision Engineer in the OpenAI Dev Day held in New Delhi, India.}
      \resumeItem{Managing the backend infrastructure of the organization to handle resources better.}
      \resumeItem{Crafted terraform recipes for AWS to deploy a fully-managed spot-requested EC2 instance for running Nvidia's Isaac Sim and Isaac Lab simulation software on the cloud, increasing accessibility by 100\%.}
      \resumeItem{Configured the AWS platform with policies, roles, and dashboards to seamlessly manage the organization's resources.}
      \resumeItem{Integrated Mistral7B in RoboGPT to enhance response latency, resulting in a \$3000 monthly savings on Azure OpenAI services.}
      \resumeItem{Constrained the LLM models in RoboGPT by adding guardrails to safeguard model responses against their intended behavior.}
      \resumeItem{Experimented with several prompt engineering techniques for Phi3-mini LLM, reducing hallucinations with tool usage by 40\%.}
      \resumeItem{Contributed to skill training features via code templates and system prompting, enabling real-time learning for new robot skills.}
      \resumeItem{Researched and tested several Small Language Models for offline AI capabilities, cutting infrastructure operation costs by 20\%.}
      \resumeItem{Reviewed and tested research papers on synthetic data generation, diversifying data collection capabilities by 60\%.}
      % \resumeItem{Deployed RoboGPT on an edge device (Jetson Nano) to minimize cloud deployment cost by 80\%}
      % \resumeItem{Managed the company's cloud infrastructure improving resource handling by 70\%.}
      % \resumeItem{Designed and maintained the AI module of the company's flagship software for robots (\href{https://robogpt.orangewood.co}{RoboGPT}).}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{OpenBB Finance} $|$ \footnotesize\emph{Junior Software Engineer - Platform}}{July 2023 -- March 2024}
    \resumeItemListStart
      \resumeItem{Designed ETL/data pipelines for the company's flagship enterprise software (\href{https://openbb.co/products/pro}{OpenBB Terminal Pro}).}
      \resumeItem{Maintained data standardization from over five data providers, ensuring high data quality and consistency.}
      \resumeItem{Engineered two automation scripts for the open-source software (\href{https://github.com/OpenBB-finance/OpenBB}{OpenBB Platform}) installation, improving setup time by 70\%.}
      \resumeItem{Overhauled public documentation based on user and internal feedback, improving accessibility and readability by 30\%.}
      \resumeItem{Launched ten Python packages of different data providers for the Platform, expanding data coverage on the Platform by 40\%.}
      \resumeItem{Developed custom deprecation messages in extensions, significantly enhancing user interface and experience.}
      \resumeItem{Devised a JSON structure to gather information about functions in Python packages, achieving 100\% automation in data syncing.}
      \resumeItem{Productionized website documentation generation using the JSON structure, streamlining deployment time by 70\%.}
      \resumeItem{Maintained GitHub CI workflows to ensure development changes, code quality, and consistency.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Miko} $|$ \footnotesize\emph{Data Engineering Intern}}{May 2023 -- August 2023}
    \resumeItemListStart
      \resumeItem{Deployed a data pipeline for Mixpanel API, enabling 24x7 data collection on AWS, streamlining analysis processes.}
      \resumeItem{Audited databases to identify and rectify inconsistencies, ensuring high data integrity.}
      \resumeItem{Developed a proof of concept for a payment data pipeline using Chargebee API, facilitating efficient data collection.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Rosenblatt Securities} $|$ \footnotesize\emph{Software Developer Intern}}{March 2022 -- April 2022}
    \resumeItemListStart
      \resumeItem{Deployed a data pipeline for time series data using DeFiLlama and CoinGecko APIs, increasing extraction efficiency by 30\%.}
      \resumeItem{Analyzed time series data for consistency, accuracy, and non-redundancy, enhancing analytics performance by 60\%.}
      \resumeItem{Developed a process to generate Excel workbooks with time series data for the top five cryptocurrencies for further evaluation.}
    \resumeItemListEnd

    % \resumeProjectHeading
    % {\textbf{Agile Social Learning 360} $|$ \footnotesize\emph{Software Developer Intern}}{January 2021 -- June 2021}
    % \resumeItemListStart
    %   \resumeItem{Optimized AWS CloudFormation and VPC configurations for deploying user-specific virtual instances, reducing deployment times by 25\% and costs by 20\%.}
    %   \resumeItem{Enhanced security and connectivity within AWS environments using AWS VPC, Lambda, and IAM, maintaining a zero-incident security record.}
    %   \resumeItem{Managed data warehouse integration, streamlining data loading from AWS S3 to AWS Redshift, boosting data retrieval speeds by 42\% and saving \$100 per month in data streaming costs.}
    %   \resumeItem{Created AWS configuration diagrams on a client-needs basis, ensuring easier deployment and management.}
    % \resumeItemListEnd

    % \resumeProjectHeading
    % {\textbf{Lovely Professional University} $|$ \footnotesize\emph{Research Assistant}}{February 2019 -- December 2020}
    % \resumeItemListStart
    %   \resumeItem{Extracted and transformed a comprehensive dataset from several research papers, improving model predictions by 10\%.}
    %   \resumeItem{Tuned 15+ machine learning models using sklearn and XGBoost, benchmarking performance against the augmented dataset.}
    %   \resumeItem{Performed literature review of Adaptive Neuro-Fuzzy Inference System variants for application in Agile story points prediction.}
    %   \resumeItem{Produced an optimization algorithm called Energy Efficient Bat (EEBAT) algorithm based on a swarm of bats utilizing their energy for exploration and exploitation effectively using their mean fitness as the energy source.}
    %   \resumeItem{Optimized the Adaptive Neuro-Fuzzy Inference System hyperparameters via the EEBAT algorithm, achieving 97\% accuracy.}
    %   \resumeItem{Contributed to the doctoral thesis by performing code analysis and literature review of several variants of Bat optimization algorithm, culminating into a research paper publication in \href{https://www.nature.com/articles/s41598-022-11565-2}{Nature}.}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd

% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{\href{https://www.agentops.ai/}{AgentOps}} $|$ \footnotesize\emph{Open Source observability platform for AI agents}}{}
        \resumeItemListStart
            \resumeItem{Active maintainer of the AgentOps-AI repositories, focusing mainly on the AgentOps and tokencost products.}
            \resumeItem{Engineering the data pipelines using OpenTelemetry Python SDK to allow custom dashboards via the \href{https://github.com/agentops-ai/jaiqu/}{Jaiqu} tool.}
            \resumeItem{Integrated support for OpenAI Assistants, Mistral, and LlamaStack Python SDK.}
            \resumeItem{Developed advanced support for \href{https://github.com/microsoft/TaskWeaver}{Microsoft TaskWeaver}, a code-first agent framework.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{\href{https://defillama-curl.readthedocs.io/}{DeFiLlama-Curl}} $|$ \footnotesize\emph{Top downloaded python library to fetch DeFiLlama data via PycURL}}{}
        \resumeItemListStart
            \resumeItem{Incorporated PycURL to fetch data from DeFiLlama REST APIs, enhancing data retrieval performance by 80\%.}
            \resumeItem{Optimized data retrieval speed by implementing multithreading, reducing fetch time by 50\%.}
        \resumeItemListEnd
    
        \resumeProjectHeading
        {\textbf{\href{https://github.com/katsamapol/Adversarial-Attack-to-Image-Caption}{Adversarial Attack on Image Captioning Models}} $|$ \footnotesize\emph{Evaluated the security of image captioning models through adversarial attacks}}{}
        \resumeItemListStart
            \resumeItem{Developed an image captioning model using an Encoder-Decoder-based Attention mechanism with Beam Search.}
            \resumeItem{Implemented adversarial attack models using ResNet-50, ResNet-101, and ResNet-152 as encoders.}
            \resumeItem{Trained models on MSCOCO 2014 and Flickr8k datasets.}
            \resumeItem{Achieved a 69\% success rate in white-box attacks on the models.}
            \resumeItem{Reduced BLEU-4 score from 32 to 25 through black-box attacks on the CLIPCap captioning model.}
        \resumeItemListEnd
          
        \resumeProjectHeading
        {\textbf{\href{https://github.com/the-praxs/dl-benchmark}{Benchmarking Deep Learning Ecosystems on HPC}} $|$ \footnotesize\emph{Performance analysis of Flux and PyTorch frameworks on HPCs}}{}
        \resumeItemListStart
            \resumeItem{Developed and trained LeNet and ResNet-50 models on MNIST and FashionMNIST datasets.}
            \resumeItem{Benchmark accuracy and performance metrics against batch size and number of workers.}
            \resumeItem{Engineered 10 test suites for CUDA and non-CUDA HPCs.}
            \resumeItem{Concluded that Flux offers superior performance but PyTorch has stronger community support.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{\href{https://medium.com/@praxs/defillama-curl-python-api-a413b59157b0}{Blockchain Protocol Analysis and Prediction}} $|$ \footnotesize\emph{Analyzing and predicting trends of popular blockchain protocols}}{}
        \resumeItemListStart
            \resumeItem{Deployed a Python script for continuous data retrieval from DeFiLlama, storing data in a database.}
            \resumeItem{Performed exploratory data analysis (EDA) on market trends, trading volumes, and values of top chains.}
            \resumeItem{Utilized Prophet Library to predict market trends for the next 3 months with 95\% accuracy.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{\href{https://github.com/the-praxs/Insurance-Modeling}{Insurance Charges Prediction}} $|$ \footnotesize\emph{Predicting insurance charges based on analyzed data}}{}
        \resumeItemListStart
            \resumeItem{Conducted EDA to analyze factors affecting insurance charges, obtaining key insights.}
            \resumeItem{Enhanced model accuracy by 15\% via feature engineering, including clustering similar families and creating two new features.}
            \resumeItem{Compared performance of Linear, Polynomial, Ridge, Gradient Boost, XGBoost, and CatBoost regression models.}
            \resumeItem{Optimized Gradient Boost hyperparameters to achieve maximum accuracy of 85.44\%.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{\href{https://github.com/the-praxs/Stock-Price-Movement}{Stock Price Movement}} $|$ \footnotesize\emph{Evaluated the impact of quarterly earnings reports on stock price movement}}{}
        \resumeItemListStart
            \resumeItem{Engineered a CLI application to download, calculate, and plot data using GNUPlot.}
            \resumeItem{Implemented liburl to fetch adjusted close prices for Russell 3000 stocks and IWV via EODHD.}
            \resumeItem{Analyzed stocks based on earnings and Zacks consensus estimates, sorting them into three groups.}
            \resumeItem{Developed a Bootstrap class to calculate AAR, AAR-STD, CAAR, and CAAR-STD for each stock group.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{\href{https://github.com/hawk-praxs/dog-breed-classifier}{Dog Breed Classifier}} $|$ \footnotesize\emph{Deep learning model for classifying dog breeds from images}}{}
        \resumeItemListStart
            \resumeItem{Augmented Stanford Dogs dataset from 120 to 134 breeds, improving data quality and size.}
            \resumeItem{Developed a face detector using ResNet-50, achieving 100\% accuracy in detecting dog faces.}
            \resumeItem{Trained a transfer learning-based classifier to 87\% accuracy, outperforming the ResNet-50+FT+DA model.}
            \resumeItem{Deployed the model using AWS SageMaker and AWS Lambda, facilitating end-user access through APIs.}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% -------------------- Publications--------------------
\section{Publications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeLink{https://link.springer.com/chapter/10.1007/978-3-031-28073-3_50}{Attacking Compressed Vision Transformers, 2023}
    \resumeLink{https://dl.acm.org/doi/abs/10.1155/2021/6455592}{Taxonomy of Adaptive Neuro-Fuzzy Inference Systems in Modern Engineering Sciences, Hindawi, 2021}
    \resumeLink{https://www.degruyter.com/document/doi/10.1515/9783110676112-009/html}{Nature-inspired optimization techniques, Nature-inspired Optimization Algorithms, De-Gruyter, 2021}
\end{itemize}

% -------------------- Certifications--------------------
\section{Certifications}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \resumeLink{https://www.udacity.com/course/aws-machine-learning-engineer-nanodegree--nd189}{Machine Learning Engineer Nanodegree, Udacity}
        \resumeLink{https://www.coursera.org/account/accomplishments/specialization/BXK6MS6YPXB9}{Mathematics for Machine Learning Specialization, Coursera}
        \resumeLink{https://wqu.thedataincubator.com/certificate/5638022657736704}{Applied Data Science Module Unit 2 (Honors) - Machine Learning and Statistical Analysis}
        \resumeLink{https://wqu.thedataincubator.com/certificate/5638022657736704_full}{Applied Data Science Module Unit 1 (Honors)}
    \end{itemize}


 \end{document}
